Earth at night*\\ {\footnotesize \textsuperscript{*}The visualisation of average radiance in specific area}

### 2021-09-16 paper/main.tex
update order

\subsection{Oauth github}
GitHub's OAuth implementation supports standard authorization code type or OAuth2 device Authorization
for apps that do not have access to a web browser. If you want to skip authorizing your app in
standard method, for example, when testing app, you are able to apply the non-web application flow/
If you want to create an OAuth Application in GitHub, client will need to log into Github, visit
the Applications page under your organisation's settings, click Register 'New Application',
set HomePage URL: Enter the Quay Enterprise URL as the HomePage URL, finally, save your settings by
clicking the Register application button. An OAuth App could be used as an identity provider by enabling
a "Login with GitHub" as for the authenticated user. Do not build an OAuth app if you want your
application to act on a single repository. With the repo OAuth scope, OAuth apps is able to act on
all of the authenticated user's repositories. If you want to register for OAuth application,
in the upper-right corner of any page, click your profile photo, then click Setting, in the
left side bar, click Developer settings, in the left side bar, click OAuth Apps, click New
OAuth App, in Application Name, type the name of your app.OAuth is a standard that apps can
use to provide client applications with 'secure delegated access'. OAuth works over HTTPS and
authorizes devices, APIs, servers, and applications with access tokens rather than credentials,
such as your client ID, yout client secret key. Nowadays, OAuth2 is the most widely used form of
OAuth.

@@

Ansible is a famous open source deployment platform, which is convenient to enable the infrastructure as code (IaC). 
It is the main tool to deploy most of the services in this project. Especially, a single EC2 instance with public 
IP is provided for it. But AWS service has to provision services by aws-cli instead of Ansible itself. There are still 
some libaries providing these functions but mostly are from external part. Ansible does not require
a single controlling machine where orchestration begins. Ansible works against multiple systems in your infrastructure
by selecting portions of Ansible's inventory, stored as edit-able, version-able ASCII text files.

@@

\subsection{Frontend}
The Frontend of this project is consist of two part, for example, login page and homepage.
we can sign in with github, and then it turn to the third party authentication and the user
will ask to verify some of their user information like user github account, then we will
be redirected to A2 Inc homepage, from this website, we are able to see that A2 Inc logo
is 'do impossible', after that, it have three different regions, for example, New Zealand,
China and Middle East. which has been marked on the world map. Next, we are allowed to select
three time modes, for example, Year, Month, Day, which would determine how that line chart
perform, from the line chart we are able to see that the radiance or pixels of the sampled
regions vary in every year from 2012 to 2020, the data was based on the World Bank Nighttime
Light, and stored it in Amazon Web Services. Usually the radiance/pixels line chart is likely
to vary much more frequent from Year to Day. When mouse move to the graph, Red rectangles
is possible to turn to Red, which shows the researched area. Blue Rectangles represent some
place we chose in order to researching data.

@@

It is important that some tools let the team work like a native team. All of the team members are from China, but nobody knew each other before. 
So at the first day, the IM platform named Lark, which was widely used in the work place in China, was chosen by team members. Java is the first 
language in the team because team members are almost good at it. By Github, all of the code can be easily shared with members and easily taken 
control of its version. Remote cooperation is not a easy thing, so team members create a event for vedio meeting everyday. At the same time, it 
is also the agile standup meeting everyday. With the development and research process, some members have to stop to learn more things about the 
lack of relative knowledge. For example, none of members are good at some key technologies, such as geospatial imagery processing, Vue, AWS usage. 
So the development plan was always disrupted because of the learning. Thanks to the agile method, the development is not influenced too much by 
these disruptions.

@@

@@

S3 public data are also used in this demo. Everyone can read this data, so there is no special permission setting in this demo. RDS MySQL provided the authentication 
by itself. The user and password can be used for the RDS MySQL. Moreover, the password is automatically generated and rotated by a Lambda function. That is 
very good practical design in AWS.

@@

Because the user data stored in RDS is the highly sensitive data in this demo, only the Java instances are allowed to visit it. And the entitlement matrix 
is shown as Fig.~\ref{matrix}

@@

There are some accurate permission control methods provided by MySQL. The entitlement matrix is made by the MySQL privileges. Admin account is the supper administrator 
which is managed by the project manager role. It is responsible for the management about database creating and auditing. And also, resource based policies provided 
by IAM also give a basic data security, which is the role named AWSServiceRoleForRDS allowing the EC2 instance to visit RDS. At the application layer, the guest role 
have no permission to read the user data. At the data shring layer, the user data has no need to share, so it does not take it into consideration. At the auditing layer, 
project manager is responsible for the daily auditing of the account based auditing.

@@

For the data at rest encryption, RDS can enable the encryption when the database is created. And the key is stored in KMS. It is the cloud handles encryption.

For the data in motion encryption, https is the most useful method between users and this demo.

@@

The second step is the subnet design, which is shown as Fig.~\ref{subnet}. There are there different subnets using for services in different layers. And also, 
these subnet configurations help the step one to isolate the public network environment. The subnets named Intranet2 and Intranet3 are the isolated frontend 
instances. The benefit of this design is isolate the same functions into different partitions. When a part of entire demo are hacked, it is easy 
to close this part to avoid more damage. The third subnet is the core subnet which is connected with database.

@@

\textbf{Writing contribution includs:} The previous 8 paragraphs of solution summary, and H, I, J, 
    K subsections in it. The A, E, G subsections of proposed solution. The section of security 
    Considerations. The section of actual AWS expenditure.

@@

\textbf{Writing contribution includs:}

@@

\subsection{SiXiang Xiong}
\textbf{Role and Tasks:} BE, Testing
From my perspective, I have study many methods of writing user login and third party login,
finally learning how to implement the third party login with github as for our website,
usually we use OAuth2, springboot, then select java to develop, in this project, I help to test
this website though postman.
\textbf{Writing contribution includs:}

\subsection{Wenjie Tong} 
\textbf{Role and Tasks:} UI designer,Data Researcher, Testing.
    In my part of this project, I am playing a role of UI designer,Data Researcher and function 
    tester. 
    Implementing part of the contribution:
    UI desgin is based on functions to develop the web pages.
    Data reseach regarding with World Bank Light Every Light doucument,and I have done further 
    study to understand the related knowledge about DSMP-OLS and VIISR-DNB data.
    I will take a part of testing task to ensure the functionality of our project.

>>>>

@@

Ansible is a famous open source deployment platform, which is convenient to enable the infrastructure as code (IaC). 
It is the main tool to deploy most of the services in this project. Especially, a single EC2 instance with public 
IP is provided for it. But AWS service has to provision services by aws-cli instead of Ansible itself. There are still 
some libaries providing these functions but mostly are from external part.

@@

\subsection{Frontend}

@@

It is important that some tools let the team work like a native team. All of the team members are from China, but nobody knew each other before. 
So at the first day, the IM platform named Lark, which was widely used in the work place in China, was chosen by team members. Java is the first 
language in the team because team members are almost good at it. By Github, all of the code can be easily shared with members and easily taken 
control of its version. Remote cooperation is not a easy thing, so team members create a event for video meeting everyday. At the same time, it 
is also the agile standup meeting everyday. With the development and research process, some members have to stop to learn more things about the 
lack of relative knowledge. For example, none of members are good at some key technologies, such as geospatial imagery processing, Vue, AWS usage. 
So the development plan was always disrupted because of the learning. Thanks to the agile method, the development is not influenced too much by 
these disruptions.

@@

The second step is the subnet design, which is shown as Fig.~\ref{subnet}. There are 3 different subnets using for services in different layers. And also, 
these subnet configurations help the step 1 to isolate the public network environment. The subnets named Intranet2 and Intranet3 are the isolated frontend 
instances. The benefit of this design is isolate the same functions into different partitions. When a part of entire demo are hacked, it is easy 
to close this part to avoid more damage. The third subnet is the core subnet which is connected with database.

@@

S3 public data are also used in this demo. Everyone can read this data, so there is no special permission setting in this demo. RDS MySQL provided the authentication 
by itself. The user and password can be used for the RDS MySQL. Moreover, the password is automatically generated and rotated by a Lambda function. That is a  
very good practical design in AWS.

@@

Because the user data stored in RDS is the highly sensitive data in this demo, only the Java instances are allowed to visit it. And the entitlement matrix 
is shown as Fig.~\ref{matrix}.

@@

There are some accurate permission control methods provided by MySQL. The entitlement matrix is made by the MySQL privileges. Admin account is the supper administrator 
which is managed by the project manager role. It is responsible for the management about database creating and auditing. And also, resource based policies provided 
by IAM also give a basic data security, which is the role named AWSServiceRoleForRDS allowing the EC2 instance to visit RDS. At the application layer, the guest role 
have no permission to read the user data. At the data sharing layer, the user data has no need to share, so it does not take it into consideration. At the auditing layer, 
project manager is responsible for the daily work of the account based auditing.

@@

For the data at rest encryption, RDS can enable the encryption when the database is created. And the key is stored in KMS. It is the cloud handles encryption. Actually, it 
is not enabled in this demo because there are not any extremely sensitive data like password and so on.

For the data in motion encryption, https is the most useful method between users and this demo. And also, Github Oauth provides a safe method to identify the user. When 
users follow the Github login url to get the one time code, they send the code to this demo, and this demo will visit Github api with the code by the Oauth2 protocol. All the 
process are protected by Github design. After the identifying of the user, a session could be stored in server, and generating a new encrypted cookie named JSEESIONID. With is 
cookie in every following visit, this demo can ensure user login status.

@@

@@

\textbf{Writing contribution includs:} The previous 8 paragraphs of solution summary, and F, G, H, I, J 
    subsections in it. The A, E, G subsections of proposed solution. The section of security 
    Considerations. The section of actual AWS expenditure.

@@

\textbf{Writing contribution includs:} The D, E subsections of solution summary. The B section of proposed solution.

@@

\subsection{SiXiang Xiong}
\textbf{Role and Tasks:} BE, Testing.

From my perspective, I have study many methods of writing user login and third party login,
finally learning how to implement the third party login with github as for our website,
usually we use OAuth2, springboot, then select java to develop, in this project, I help to test
this website though postman.

\textbf{Writing contribution includs:} The C, F subsections of proposed solution.

\subsection{Wenjie Tong} 
\textbf{Role and Tasks:} UI designer,Data Researcher, Testing.

    In my part of this project, I am playing a role of UI designer,Data Researcher and function 
    tester. 
    Implementing part of the contribution:
    UI desgin is based on functions to develop the web pages.
    Data reseach regarding with World Bank Light Every Light doucument,and I have done further 
    study to understand the related knowledge about DSMP-OLS and VIISR-DNB data.
    I will take a part of testing task to ensure the functionality of our project.
